---
title: "Developing Data Products Course Project"
author: "Denise Wong"
date: "1 October 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The purpose of this assignment was to build a web app using Shiny.  


Data for this project was sourced from Kaggle  
https://www.kaggle.com/koki25ando/tabelog-restaurant-review-dataset 


My app allows you to find the restaurants around your closest train station based on a maximum price limit. 



The materials can be found in:  
Web app: https://denisewong1.shinyapps.io/myshinyapp/  
GitHub Repo: https://github.com/denisewong1/ShinyApp   


## ui.R

There are two inputs expected from the user - the station name and the maximum price range - via a drop down box and a slider.  


```{r, eval=FALSE}
  sidebarLayout(
    sidebarPanel(
        selectInput("station", "Nearest Station:", 
            choices=idStation),
        hr(),
        helpText(" "),
        hr(),
        sliderInput("slider1", "Max Price", 2000, 5000, 4000),
        hr()
    )
```



## server.R

This code snippet evaluates the subset of restaurants which are closest to the station selected 'station' and below the maximum price range 'slider' from the inputs in the ui.R code.  

The subsetted data is displayed as leaflet map.  

```{r, eval=FALSE}
data <- reactive({
    x <- subset(df, Station==input$station & PriceHigh < input$slider1)
})
```


This code snippet calculates the number of restaurants in the area based on the selection criteria and outputs the message to the main plot panel.    

```{r, eval=FALSE}
nMsg <- paste("Restaurants in your price range : ",NROW(dfRest),sep="")
output$message1 <- renderText({
    nMsg
})
```


## Try it now!  


Web app: https://denisewong1.shinyapps.io/myshinyapp/  



GitHub Repo: https://github.com/denisewong1/ShinyApp  





